### 2017-03-31 paper/evaluation.tex

\Jbc{Pending updates here}
Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-med.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\

    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Medium & 17 & 20 & 7 \\
        Long   &  9 & 14 & 5 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{missing caption}}    
    \end{subfigure}%

@@

\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely 0.41s for \medg{} projects and 0.23s for
\longg{} projects.  Note that correlation between cost of test suites
and cost of their individual tests is not to be expected.  The
standard deviation ($\sigma$) associated with each ditribution was
relatively low.  Figure~\ref{fig:sd} shows the number of projects
within specific ranges of $\sigma$ values.  We also observed that
projects with very high standard deviations may or may not be
indicative of monopolization of execution by a small number of tests.
For example, the highest value of $\sigma$ ocurred in project
\CodeIn{wildfly-swarm}, whose test suite was classified as
long-running.  This project contains only 65 tests, 62 of which take
less than 0.5s to run, 1 of which takes nearly 3s to run, and 2 of
which take 40m to run.  This is an example where test suite
parallelization may not be very beneficial as $>$99\% execution cost
is dominated by only 3\% of the tests.  Without these two tests this
project would have been classified as short-running.  A closer
inspection in the data indicates that the project
\CodeIn{wildfly-swarm} was an extreme case; we did not find projects
with similar characteristics of time monopolization.  Project
\CodeIn{jenkinsci.gerrit-trigger-plugin} is also classified as
long-running and has the second highest value of $\sigma$.  For this
project, however, cost is distributed more smoothly across 529 tests,
of which 119 take more than 1s to run.

>>>>

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, parallelism by itself does
not assure speedups on those projects.  One sensible factor that is
important to the effectiveness of low-level parallelism is the
distribution of test costs in the test suite.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{plots/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group}
    \end{subfigure}\\
    \vspace{2.5ex}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \begin{tabular}{rrrr}
        \toprule
        & $\sigma\leq1$ & $1<\sigma\leq5$ & $\sigma\ge5$ \\
        \midrule    
        Medium & 17 & 20 & 7 \\
        Long   &  9 & 14 & 5 \\
        \bottomrule
      \end{tabular}
      \caption{\label{fig:sd}\Fix{adjust values}}    
    \end{subfigure}%

@@

\sloppy Figures~\ref{fig:medtcost} and~\ref{fig:longtcost} show the
time distribution of tests per project.  We observed that the average
median value of execution cost for a test was relatively small (dashed
horizontal red lines), namely \Fix{0.41s} for \medg{} projects and
\Fix{0.23s} for \longg{} projects.  Note that correlation between cost
of test suites and cost of their individual tests is not to be
expected.  The standard deviation ($\sigma$) associated with each
distribution was relatively low.  Figure~\ref{fig:sd} shows the number
of projects within specific ranges of $\sigma$ values.  We also
observed that projects with very high standard deviations may or may
not be indicative of monopolization of execution by a small number of
tests.  For example, the highest value of $\sigma$ occurred in project
\CodeIn{wildfly-swarm}, whose test suite was classified as
long-running.  This project contains only \Fix{65} tests, \Fix{62} of
which take less than \Fix{0.5s} to run, \Fix{1} of which takes nearly
\Fix{3s} to run, and \Fix{2} of which take \Fix{40m} to run.  This is
an example where test suite parallelization may not be very beneficial
as \Fix{$>$99\%} execution cost is dominated by only \Fix{3\%} of the
tests.  Without these two tests this project would have been
classified as short-running.  A closer inspection in the data
indicates that the project \CodeIn{wildfly-swarm} was an extreme case;
we did not find projects with similar characteristics of time
monopolization.  Project \CodeIn{jenkinsci.gerrit-trigger-plugin} is
also classified as long-running and has the second highest value of
$\sigma$.  For this project, however, cost is distributed more
smoothly across \Fix{529} tests, of which \Fix{119} take more than
\Fix{1s} to run.
